On Extending a Full-Sharing Multithreaded Tabling Design with Batched Scheduling

### 2015-05-26 paper.tex
paper -> revising 1

\begin{figure}[!ht]
%\vspace{-0.5\intextsep}
\centering
\includegraphics[width=9.5cm]{figures/yap-mt.pdf}
\caption{Yap's multithreaded table space organization for the NS and FS designs}
\label{fig_yap_mt_support}
%\vspace{-1.0\intextsep}
\end{figure}

@@

\begin{figure}[!ht]
%\vspace{-\intextsep}
\centering
\includegraphics[width=10.5cm]{figures/pcc.pdf}
\caption{PAC's data structures for (a) private and (b) public
  chaining}
\label{fig_tabtries_pcc}
%\vspace{-1.0\intextsep}
\end{figure}

@@

Going back to Fig.~\ref{fig_tabtries_pcc}(a), the PAC's data
structures represent then two different situations where threads can
be evaluating a subgoal call. Thread $T_1$ has only found one answer
and it is using a direct answer chaining to access the node
$LN_1$. Thread $T_{k-1}$ was already found three answers for the
subgoal call and it is using the hash trie mechanism within its
private chaining. Please note that the answer nodes are still chained
between themselves, thus that repeated calls belonging to thread
$T_{k-1}$ can consume the answers as in the original mechanism.

Figure~\ref{fig_tabtries_pcc}(b) shows the state of the subgoal call
after completion. When a thread $T$ completes a subgoal call, it frees
its private consumer structures, but before doing that, it checks
whether another thread as already marked the subgoal as completed. If
no other thread has done that, then thread $T$ not only follows its
private chaining mechanism as it would for freeing its private nodes,
but also, follows the pointers to the answer trie leaf nodes in order
to create a chain inside the answer trie. Since this procedure is done
inside a critical region, no more than one thread can be doing this
chaining process. Thus, in Fig.~\ref{fig_tabtries_pcc}(b), we are
showing the situation where the subgoal call is completed and both
threads $T_1$ and $T_{k-1}$ have already chained the leaf nodes inside
the answer trie and removed their private chaining structures.

@@

\setlength{\tabcolsep}{12pt}
\begin{table}[!ht]
\centering
\caption{Overhead ratios, when compared with the NS design with $1$
  thread (running with local scheduling and without TabMalloc) for the NS
  and FS designs (with TabMalloc), when running 1, 8, 16, 24 and 32
  threads with local and batched scheduling (best ratios by row and by
  design for the Minimum, Average and Maximum are in bold)}
\begin{tabular}{ll||cc|cc}
\multicolumn{2}{c||}{\multirow{2}{*}{\bf Threads}} &
\multicolumn{2}{c|}{\multirow{1}{*}{\bf NS}} &
\multicolumn{2}{|c}{\multirow{1}{*}{\bf FS}}\\ \cline{3-6}
& 
& \multicolumn{1}{c}{\bf Local}
& \multicolumn{1}{c}{\bf Batched}
& \multicolumn{1}{|c}{\bf Local}
& \multicolumn{1}{c}{\bf Batched (PAC)}\\
\hline\hline
\multirow{4}{*}{\bf 1}
& {\bf Min }& {\bf 0.53}& 0.55& 1.01& {\bf 0.95}\\
& {\bf Avg }& {\bf 0.78}& 0.82& {\bf 1.30}& 1.46\\
& {\bf Max }& 1.06& {\bf 1.05}& {\bf 1.76}& 2.33\\
& {\bf StD }& 0.15& 0.14& 0.22& 0.44\\
\hline
\multirow{4}{*}{\bf 8}
& {\bf Min }& 0.66& {\bf 0.63}& 1.16&{\bf  0.99}\\
& {\bf Avg }& {\bf 0.85}& 0.88& {\bf 1.88}& 1.95\\
& {\bf Max }& {\bf 1.12}& 1.14& {\bf 2.82}& 3.49\\
& {\bf StD }& 0.13& 0.14& 0.60& 0.79\\
\hline
\multirow{4}{*}{\bf 16}
& {\bf Min }& 0.85& {\bf 0.75}& 1.17& {\bf 1.06}\\
& {\bf Avg }& {\bf 0.98}& 1.00& {\bf 1.97}& 2.08\\
& {\bf Max }& {\bf 1.16}& 1.31& {\bf 3.14}& 3.69\\
& {\bf StD }& 0.09& 0.17& 0.65& 0.83\\
\hline
\multirow{4}{*}{\bf 24}
& {\bf Min }& {\bf 0.91}& 0.93& 1.16& {\bf 1.09}\\
& {\bf Avg }& {\bf 1.15}& 1.16& {\bf 2.06}& 2.19\\
& {\bf Max }& 1.72& {\bf 1.60}& {\bf 3.49}& 4.08\\
& {\bf StD }& 0.20& 0.21& 0.70& 0.91\\
\hline
\multirow{4}{*}{\bf 32}
& {\bf Min }& 1.05& {\bf 1.04}& 1.33& {\bf 1.26}\\
& {\bf Avg }& 1.51& {\bf 1.49}& {\bf 2.24}& 2.41\\
& {\bf Max }& {\bf 2.52}& 2.63& {\bf 3.71}& 4.51\\
& {\bf StD }& 0.45& 0.45& 0.74& 1.02\\
\end{tabular}
\label{tab_batched_overhead}
\end{table}

>>>>

\begin{figure}[!ht]
\vspace{-0.5\intextsep}
\centering
\includegraphics[width=9.5cm]{figures/yap-mt.pdf}
\caption{Yap's multithreaded table space organization for the NS and FS designs}
\label{fig_yap_mt_support}
\vspace{-1.0\intextsep}
\end{figure}

@@

\begin{figure}[!ht]
\vspace{-\intextsep}
\centering
\includegraphics[width=10.5cm]{figures/pcc.pdf}
\caption{PAC's data structures for (a) private and (b) public
  chaining}
\label{fig_tabtries_pcc}
\vspace{-0.5\intextsep}
\end{figure}

@@

Going back to Fig.~\ref{fig_tabtries_pcc}(a), the PAC's data
structures represent then two different situations where threads can
be evaluating a subgoal call. Thread $T_1$ has only found one answer
and it is using a direct answer chaining to access the node
$LN_1$. Thread $T_{k-2}$ was already found three answers for the
subgoal call and it is using the hash trie mechanism within its
private chaining. Please note that the answer nodes are still chained
between themselves, thus that repeated calls belonging to thread
$T_{k-2}$ can consume the answers as in the original mechanism.

Figure~\ref{fig_tabtries_pcc}(b) shows the state of the subgoal call
after completion. When a thread $T$ completes a subgoal call, it frees
its private consumer structures, but before doing that, it checks
whether another thread as already marked the subgoal as completed. If
no other thread has done that, then thread $T$ not only follows its
private chaining mechanism as it would for freeing its private nodes,
but also, follows the pointers to the answer trie leaf nodes in order
to create a chain inside the answer trie. Since this procedure is done
inside a critical region, no more than one thread can be doing this
chaining process. Thus, in Fig.~\ref{fig_tabtries_pcc}(b), we are
showing the situation where the subgoal call is completed and both
threads $T_1$ and $T_{k-2}$ have already chained the leaf nodes inside
the answer trie and removed their private chaining structures.

@@

\setlength{\tabcolsep}{12pt}
\begin{table}[!ht]
\centering
\caption{Overhead ratios, when compared with the NS design with $1$
  thread (running with local scheduling and without TabMalloc) for the NS
  and FS designs (with TabMalloc), when running 1, 8, 16, 24 and 32
  threads with local and batched scheduling (best ratios by row and by
  design for the Minimum, Average and Maximum are in bold)}
\begin{tabular}{ll||cc|cc}
\multicolumn{2}{c||}{\multirow{2}{*}{\bf Threads}} &
\multicolumn{2}{c|}{\multirow{1}{*}{\bf NS}} &
\multicolumn{2}{|c}{\multirow{1}{*}{\bf FS}}\\ \cline{3-6}
& 
& \multicolumn{1}{c}{\bf Local}
& \multicolumn{1}{c}{\bf Batched}
& \multicolumn{1}{|c}{\bf Local}
& \multicolumn{1}{c}{\bf Batched}\\
\hline\hline
\multirow{4}{*}{\bf 1}
& {\bf Min }& {\bf 0.53}& 0.55& 1.01& {\bf 0.95}\\
& {\bf Avg }& {\bf 0.78}& 0.82& {\bf 1.30}& 1.46\\
& {\bf Max }& 1.06& {\bf 1.05}& {\bf 1.76}& 2.33\\
& {\bf StD }& 0.15& 0.14& 0.22& 0.44\\
\hline
\multirow{4}{*}{\bf 8}
& {\bf Min }& 0.66& {\bf 0.63}& 1.16&{\bf  0.99}\\
& {\bf Avg }& {\bf 0.85}& 0.88& {\bf 1.88}& 1.95\\
& {\bf Max }& {\bf 1.12}& 1.14& {\bf 2.82}& 3.49\\
& {\bf StD }& 0.13& 0.14& 0.60& 0.79\\
\hline
\multirow{4}{*}{\bf 16}
& {\bf Min }& 0.85& {\bf 0.75}& 1.17& {\bf 1.06}\\
& {\bf Avg }& {\bf 0.98}& 1.00& {\bf 1.97}& 2.08\\
& {\bf Max }& {\bf 1.16}& 1.31& {\bf 3.14}& 3.69\\
& {\bf StD }& 0.09& 0.17& 0.65& 0.83\\
\hline
\multirow{4}{*}{\bf 24}
& {\bf Min }& {\bf 0.91}& 0.93& 1.16& {\bf 1.09}\\
& {\bf Avg }& {\bf 1.15}& 1.16& {\bf 2.06}& 2.19\\
& {\bf Max }& 1.72& {\bf 1.60}& {\bf 3.49}& 4.08\\
& {\bf StD }& 0.20& 0.21& 0.70& 0.91\\
\hline
\multirow{4}{*}{\bf 32}
& {\bf Min }& 1.05& {\bf 1.04}& 1.33& {\bf 1.26}\\
& {\bf Avg }& 1.51& {\bf 1.49}& {\bf 2.24}& 2.41\\
& {\bf Max }& {\bf 2.52}& 2.63& {\bf 3.71}& 4.51\\
& {\bf StD }& 0.45& 0.45& 0.74& 1.02\\
\end{tabular}
\label{tab_batched_overhead}
\end{table}
